Bootstrap learning via modular concept discovery

### 2013-04-22 drafts/ijcai2013/ijcai13.tex
Added pdfinfo to preamble.
Minor alterations to citations to get compilation to work.

@@

\author{Eyal Dechter \\
MIT\\
USA \\
edechter@mit.edu
\And
Jon Malmaud \\
MIT \\ 
USA \\
malmaud@mit.edu
\And 
Ryan P.  Adams \\
Harvard University\\
USA \\
rpa@seas.harvard.edu
\And
Joshua B. Tenenbaum \\
MIT\\
USA \\
jbt@mit.edu
}

@@

\subsection{Best-first enumeration of programs}
In order to explore the frontier of most promising programs, we need a
procedure that enumerates the $N$ most probable expressions. There has
been recent interest in this problem, most of it focused on
enumerating the shortest program satisfying some
criterion~\cite{DBLP:conf/sfp/Katayama05, DBLP:conf/aaip/YakushevJ09}. Our approach is to formulate the
problem as a best-first exploration of an AND/OR tree
(Figure~\ref{fig:andor})~\cite{nilsson1982principles, DBLP:journals/cacm/Hall73}. In
words, the enumeration procedure is best described by the following
recursion: every program is either a primitive combinator OR it is a
left child program applied to a right child program (that is, a left
child AND a right child).

@@

\setcounter{subfigure}{0} 
\begin{figure}[ht]
\centering
\includegraphics[width=1.0\linewidth]{figures/symreg3frontiers.pdf}
%\vspace{-.2cm}
\caption{Learning curves as a function of frontier size.  As frontier
  size is increased, curves plateau closer to $100\%$ performance. A
  baseline search over $150000$ expressions only hits $3\%$ of the
  tasks (dashed pink line). \label{fig:symregLearning}}
%\vspace{-.3cm}
\end{figure}
\begin{figure}[ht]
\includegraphics[width=1.07\linewidth]{figures/symRegDiffCurricula.pdf}
\caption{How do different task sets affect learning curves? Learning
  curves at frontier size of $10000$ for different task
  sets.} 
\label{fig:symregCurricula}

@@

\begin{figure}[t]
\includegraphics{./figures/tablealonedoc.pdf}
%% \vspace{-.5cm}
\caption{Some learned primitives from the circuit based Boolean
  function learning experiment. We highlight compression using $NOT$,
  $E_1$ and $E_2$. \,(a)The three elementary gates used to generate
  the task set. (b) Two higher-order primitives in the induced
  grammar. Note how $E_1$ can be used to define FALSE by taking the
  NOT function as an argument. (c) Additional common Boolean functions
  found in the learned grammar.  \label{table:booleanCircuits}}
%%\vspace{-.4cm}
\end{figure}

@@

%% \begin{table}
%% \tiny
%% \begin{tabular}[width=\linewidth]{|p{1cm}|p{2cm}|p{3.5cm}|}
%% \hline function  & CL expression & circuit  ~ \\ \hline\hline
%% ¬†¬†¬†¬†¬†¬†¬†¬†NOT¬†¬† & S NAND I¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬† &  ~

%% \begin{circuitikz}[transform shape]
%% \draw
%% (1.2,0) node[nand port, scale=.3] (nand1) {}
%% (0, 0) node (x) {x}
%% (x) -| (nand1.in 1)
%% (x) -| (nand1.in 2)
%% ;
%% \end{circuitikz}

%% \\ \hline
%% ¬†¬†¬†¬†¬†¬†¬†¬†AND¬†¬† & ((C B NAND) (B (S NAND I)))¬†¬†¬†¬†¬†¬†¬†¬†¬†¬† & ~

%% \begin{circuitikz}
%% \draw
%% (1.0,0) node[nand port, scale=.3] (nand1) {}
%% (2.0,0) node[nand port, scale=.3] (nand2) {}
%% % (0, 0) node (x) {x}
%% % (0, 0) node (y) {y}
%% node[above left=.2cm and .7cm  of nand1] (x) {x} %-- (nand1.in 1)
%% node[below left=.2cm and .7cm  of nand1] (y) {y} %-- (nand1.in 2)
%% (x) |- (nand1.in 1)
%% (y) |- (nand1.in 2)
%% (nand1.out) |- (nand2.in 1)
%% (nand1.out) |- (nand2.in 2)
%% ;
%% \end{circuitikz}
%%  \\  \hline
%% ¬†¬†¬†¬†¬†¬†¬†¬†OR¬†¬†¬† & ((B (C (B (S NAND) NAND))) (S NAND I) & ~

%% \begin{circuitikz}
%% \draw
%% (0,0) node (x) {x}
%% (0,.7) node (y) {y}

%% node[nand port, scale=.3, right=1cm of x] (nand1) {}
%% node[nand port, scale=.3, right=1cm of y] (nand2) {}
%% node[nand port, scale=.3, below right=.3cm and 1cm of nand2] (nand3) {}
%% (x) -| (nand1.in 1)
%% (x) -| (nand1.in 2)
%% (y) -| (nand2.in 1)
%% (y) -| (nand2.in 2)
%% (nand1.out) |- (nand3.in 1)
%% (nand2.out) |- (nand3.in 2)
%% ;
%% \end{circuitikz}
%%  \\  \hline\hline

%% ¬†¬†¬†¬†¬†¬†¬†¬†TRUE¬† & (S NAND) (S NAND I)¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬† & ~

%% %\begin{top}
%% \begin{circuitikz}[transform shape] 
%% \draw
%% (1, 0) node[nand port, scale=.3] (nand1) {}
%% (2,.3) node[nand port, scale=.3] (nand2) {}
%% (0, 0) node[anchor=east]  (x) {x}
%% (x) -- (.3, 0) -| (nand1.in 1)
%% (x) -- (.3, 0) -|  (nand1.in 2)
%% (x) |- (nand2.in 1)
%% (nand1.out) |- (nand2.in 2)
%% ;
%% \end{circuitikz}
%% %\end{top}
%% \\ \hline
%% ¬†¬†¬†¬†¬†¬†¬†¬†FALSE & (S B (S NAND)) (S NAND I)¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬† &  ~

%% \begin{circuitikz}[transform shape] 
%% \draw
%% (1, 0) node[nand port, scale=.3] (nand1) {}
%% (2,.3) node[nand port, scale=.3] (nand2) {}
%% node[nand port, scale=.3, right=1cm of nand2] (nand3) {} 
%% (0, 0) node[anchor=east]  (x) {x}
%% (x) -- (.3, 0) -| (nand1.in 1)
%% (x) -- (.3, 0) -|  (nand1.in 2)
%% (x) |- (nand2.in 1)
%% (nand1.out) |- (nand2.in 2)
%% (nand2.out) -| (nand3.in 1)
%% (nand2.out) -| (nand3.in 2)
%% ;
%% \end{circuitikz}
%% \\ \hline
%% ¬†¬†¬†¬†¬†¬†¬†¬†XOR¬†¬† & ((S (B C (((B (C B NAND)) S) (((B (C B NAND)) S) (B C ((B (B NAND)) NAND)))))) I)¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬† & ~

%% \begin{circuitikz}
%% \draw
%% node[nand port, scale=.3] (nand1) {}
%% node[nand port, scale=.3, above right=.3cm and 1cm of nand1] (nand2) {} 
%% node[nand port, scale=.3, below right=.3cm and 1cm of nand1] (nand3) {} 
%% node[nand port, scale=.3, right=2cm of nand1] (nand4) {} 
%% node[left=1.2cm of nand2.in 1] (x) {x}
%% node[left=1.2cm of nand3.in 2] (y) {y}
%% node[right=.2cm of nand4] (out) {}
%% (x) -| (nand1.in 1)
%% (x) -| (nand2.in 1)
%% (y) -| (nand1.in 2)
%% (y) -| (nand3.in 2)
%% (nand1.out) -| (nand2.in 2)
%% (nand1.out) -| (nand3.in 1)
%% (nand2.out) |- (nand4.in 1)
%% (nand3.out) |- (nand4.in 2)
%% (nand4.out) -- (out)
%% ;
%% \end{circuitikz}

%%  \\  \hline\hline
%% ¬†¬†¬†¬†¬†¬†¬†¬†$E_1$¬†¬†¬†  & S B (S NAND)¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬†¬† & ~

%% \begin{circuitikz}
%% \draw
%% node (x) {x}
%% node[nand port, scale=.3, right=1.5cm of x] (nand) {} 
%% node[draw=blue!75, fill=blue!20, thick, 
%%   above right=.3cm and .2cm of x, anchor=west] (f1) {$g(x)$} 
%% node[draw=blue!75, fill=blue!20, thick, right=.5cm of nand] (f2) {$g(x)$}
%% node[right=.1cm of f2] (out) {}
%% (x) -| (f1.west)
%% (x) -| (nand.in 2)
%% (f1) -| (nand.in 1)
%% (nand.out) -- (f2)
%% (f2) -- (out);
%% \end{circuitikz}

%% \\ \hline
%% $E_2$¬†¬†¬†  & B (C B NAND) S & ~

%% \begin{circuitikz}
%% \draw
%% node (x) {x} 
%% node[nand port, scale=.3, right=1.5cm of x] (nand) {} 
%% node[draw=blue!75, fill=blue!20, thick, 
%%   above right=.2cm and .3cm of x, anchor=west] (g) {$g(x)$} 
%% node[draw=blue!75, fill=blue!20, thick, 
%%   below right=.2cm and .3cm of x, anchor=west] (f) {$f(x)$} 
%% (x) -- [right=.25] (f.west)
%% (x) |- (g.west)
%% (f.east) -| (nand.in 1)
%% (g.east) -| (nand.in 2)
%% (nand.out) -- (out)
%% (x)
%% ;
%% \end{circuitikz}

%% \\ \hline

%% \end{tabular}
%% \caption{Expressions in the induced library on sets of tasks
%%   corresponding to boolean circuits synthesized from AND, OR, and NOT
%%   gates, with boolean circuits of 1, 2, or 3 inputs.}
%% \label{table:boolexpr}

%% \end{table}

%% \begin{table}[t]
%% \scriptsize
%%    \begin{tabular}{|l|l|l|}
%%     function  & CL expressions & circuit  ~ \\ \hline
%%         TRUE  & (S NAND) (S NAND I)                   & ~ \\ \hline
%%         FALSE & (S B (S NAND)) (S NAND I)             & ~ \\ \hline
%%         NOT   & S NAND I                              & \input{figures/NOT.tex} \\ \hline
%%         AND   & ((C B NAND) (B (S NAND I)))           & ~ \\ 
%%         OR    & ((B (C (B (S NAND) NAND))) (S NAND I) & ~ \\ 
%%         XOR   & ~                                     & ~ \\ 
%%         F     & S B (S NAND)                          & \input{figures/F.tex}
%%     \end{tabular}
%% \end{table}

@@

\begin{figure}
%%\vspace{-.3cm}
\includegraphics[width=\linewidth]{figures/circuitDistrComp2.png}
%%\vspace{-.6cm}
\caption{Distribution of Boolean functions among (a) the set of 1000
  circuits randomly constructed from AND, OR and NOT gates (see text);
  b) the first 1000 expressions from the grammar over expressions
  \emph{before} learning; c) the first 1000 expressions from the
  grammar over expressions \emph{after} learning. Gray levels indicate
  percent of instances (circuits/expressions) which evaluate to that
  function.\label{fig:booldistr}}
%%\vspace{-.4cm}
\end{figure}

>>>>

\usepackage{times}
\pdfinfo{
  /Title (Bootstrap learning via modular concept discovery)
  /Author (Eyal Dechter, Jon Malmaud, Ryan P. Adams, Joshua B. Tenenbaum)
}

@@

\author{Eyal Dechter \\
MIT\\
USA \\
edechter@mit.edu
\And
Jon Malmaud \\
MIT \\ 
USA \\
malmaud@mit.edu
\And 
Ryan~P.  Adams \\
Harvard University\\
USA \\
rpa@seas.harvard.edu
\And
Joshua~B. Tenenbaum \\
MIT\\
USA \\
jbt@mit.edu
}

@@

\subsection{Best-first enumeration of programs}
In order to explore the frontier of most promising programs, we need a
procedure that enumerates the $N$ most probable expressions. There has
been recent interest in this problem, most of it focused on
enumerating the shortest program satisfying some
criterion~\cite{DBLP:conf/sfp/Katayama05,DBLP:conf/aaip/YakushevJ09}. Our approach is to formulate the
problem as a best-first exploration of an AND/OR tree
(Figure~\ref{fig:andor})~\cite{nilsson1982principles,DBLP:journals/cacm/Hall73}. In
words, the enumeration procedure is best described by the following
recursion: every program is either a primitive combinator OR it is a
left child program applied to a right child program (that is, a left
child AND a right child).

@@

\setcounter{subfigure}{0} 
\begin{figure}[ht]
\centering
\includegraphics[width=1.0\linewidth]{figures/symreg3frontiers.pdf}
\caption{Learning curves as a function of frontier size.  As frontier
  size is increased, curves plateau closer to $100\%$ performance. A
  baseline search over $150000$ expressions only hits $3\%$ of the
  tasks (dashed pink line). \label{fig:symregLearning}}
\end{figure}
\begin{figure}[ht]
\includegraphics[width=1.07\linewidth]{figures/symRegDiffCurricula.pdf}
\caption{How do different task sets affect learning curves? Learning
  curves at frontier size of $10000$ for different task
  sets.} 
\label{fig:symregCurricula}

@@

\begin{figure}[t]
\includegraphics{./figures/tablealonedoc.pdf}
\caption{Some learned primitives from the circuit based Boolean
  function learning experiment. We highlight compression using $NOT$,
  $E_1$ and $E_2$. \,(a)The three elementary gates used to generate
  the task set. (b) Two higher-order primitives in the induced
  grammar. Note how $E_1$ can be used to define FALSE by taking the
  NOT function as an argument. (c) Additional common Boolean functions
  found in the learned grammar.  \label{table:booleanCircuits}}
\end{figure}

@@

@@

\begin{figure}
\includegraphics[width=\linewidth]{figures/circuitDistrComp2.png}
\caption{Distribution of Boolean functions among (a) the set of 1000
  circuits randomly constructed from AND, OR and NOT gates (see text);
  b) the first 1000 expressions from the grammar over expressions
  \emph{before} learning; c) the first 1000 expressions from the
  grammar over expressions \emph{after} learning. Gray levels indicate
  percent of instances (circuits/expressions) which evaluate to that
  function.\label{fig:booldistr}}
\end{figure}
